---
title: "Analyse attendance by-tutor, accounting for tutor group effects"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rstanarm)
library(lmerTest)
library(pander)
# devtools::install_github("mjskay/tidybayes")
library(tidybayes)
options(mc.cores = parallel::detectCores())
knitr::opts_chunk$set(echo = TRUE)
```


Arrange the raw data:

```{r, eval=F}
tut <- read_csv('tut.csv')
attend_data <- tut %>% 
  mutate(present = ifelse(attend=="1", 1, 0)) %>% 
  mutate(presentorexcused = ifelse(attend=="1"|attend=="8", 1, 0)) %>% 
  filter(Stage=="Stage 1") %>% 
  # ANONYMISE FOR NOW
  mutate(TutorSName = paste0("T", as.numeric(factor(TutorSName)))) 
write_csv(attend_data, 'anonymised.csv')
```

And if you only have the anonymised data, do this:

```{r}
attend_data <- read_csv('anonymised.csv')
```

Model binary attendance data for each individual student within tutor groups, and by tutor:

```{r, include=F, cache=T}
m1 <- stan_glmer(present~(1|TutorGroup)+(1|TutorSName), data=attend_data, family=binomial, iter=2000)
```


Plot estimated attendance by tutor (note this is NOT anonymised yet):

```{r}
attend_data %>% distinct(TutorSName, TutorGroup) %>% 
  add_fitted_samples(m1) %>% 
  group_by(TutorSName) %>% tidybayes::mean_qi(estimate) %>% 
  ungroup() %>% 
  mutate(TutorSName = forcats::fct_reorder(factor(TutorSName), estimate)) %>% 
  ggplot(aes(TutorSName, estimate, ymin=conf.low, ymax=conf.high)) + 
  geom_pointrange() + 
  coord_flip() 
```



Force the assumption that everyone had the same average tutor group. This currently blows out the tutor-level errors because we don't have enough groups per-tutor, but will contract as more data added next year:

```{r}
attend_data %>% distinct(TutorSName) %>% 
  mutate(TutorGroup=Inf) %>% 
  add_fitted_samples(m1) %>% 
  group_by(TutorSName) %>% tidybayes::mean_qi(estimate) %>% 
  ungroup() %>% 
  mutate(TutorSName = forcats::fct_reorder(factor(TutorSName), estimate)) %>% 
  ggplot(aes(TutorSName, estimate, ymin=conf.low, ymax=conf.high)) + 
  geom_pointrange() + 
  coord_flip() 
```


Are the best and worst tutors really different, even removing tutor-group effects?

```{r}
preds <- attend_data %>% distinct(TutorSName) %>% 
  mutate(TutorGroup=Inf) %>% 
  add_fitted_samples(m1) %>% 
  ungroup() %>% 
  data.table::dcast(.iteration~TutorSName, value.var="estimate")

preds %>% mean_qi(T20<T3) %>% select(-contains("conf")) %>% pander()

preds %>% mean_qi(T20-T3) %>% pander()

preds %>% 
  ggplot(aes(T20-T3)) + geom_density() + geom_vline(xintercept = 0)
```

